The forestecology R package for fitting and assessing neighborhood models of the effect of interspecific competition on the growth of trees

### 2021-08-02 paper/paper.Rmd
code line breaks

@@

  # Make predictions and compute RMSE
  shuffle_RMSE[j] <-  focal_vs_comp_scbi %>%
    mutate(growth_hat = 
             predict(comp_bayes_lm_scbi, focal_vs_comp_scbi)) %>%
    rmse(truth = growth, estimate = growth_hat) %>%
    pull(.estimate)
}

>>>>

# Associate each observation to a fold
spatial_block_scbi <- 
  spatialBlock(
    speciesData = growth_scbi, k = n_fold, 
    selection = "systematic", blocks = blocks_scbi, 
    showBlocks = FALSE, verbose = FALSE
  )

@@

  # Make predictions and compute RMSE
  shuffle_RMSE[j] <-  focal_vs_comp_scbi %>%
    mutate(
      growth_hat = predict(comp_bayes_lm_scbi, focal_vs_comp_scbi)
    ) %>%
    rmse(truth = growth, estimate = growth_hat) %>%
    pull(.estimate)
}
